---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# warlockr

The goal of warlockr is to collect useful functions for Warlocks in WoW Classic.
Right now this is mostly about simulating the DPS.
The starting point was [this](https://www.reddit.com/r/classicwow/comments/dh5r6g/so_i_made_a_warlock_shadowbolt_simulator/) Reddit post by [u/natehax](https://www.reddit.com/user/natehax/).

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cphaarmeyer/warlockr")
```
## Example

There are two main uses of the DPS simulation:

* computing how much a stat inceases your dps (stat weights)
* computing the impact of an item on your dps (compare items)

But first we set up the simulation with our current stats.

```{r example}
library(warlockr)
my_stats <- list(
  int = 223 + 31 + 12, # with buffs
  sp = 312 + 26 + 33 + 27 + 40, # shadow spell damage
  crit = 3,
  hit = 2
)
```

The `compute_statweights` function first simluates your DPS.
Then for every stat it simulates the dps with that stat increased by 1.
The weights are the difference in DPS.

```{r statweights}
set.seed(42)
my_weights <- compute_statweights(my_stats)
my_weights
```

The `compare_items` function works very similar.
As additional input it takes a list of items in which you specify the stat differences.

```{r compare}
items <- list(
  "Royal Seal of Eldre'Thalas" = list(sp = 23, crit = -2),
  "Mana Igniting Cord" = list(int = 5, sp = 12, crit = 1, hit = -1),
  "Robe of Volatile Power" = list(int = 15, sp = -23, crit = 2),
  "Burial Shawl" = list(int = 16, sp = -6),
  "Dragon's Touch" = list(int = 8, sp = -5),
  "Dark Advisor's Pendant" = list(int = -2, sp = 20, hit = -1),
  "Choker of Elightenment" = list(int = 1, sp = 18, hit = -1),
  "Choker of the Fire Lord" = list(int = -2, sp = 34, hit = -1),
  "Dragonslayer's Signet" = list(int = 5, sp = -9, crit = 1),
  "Ring of Spell Power" = list(int = -7, sp = 24),
  "Band of Forced Concentration" = list(int = 5, sp = 12, hit = 1),
  "Band of Dark Dominion" = list(int = -1, sp = 24)
)
set.seed(42)
df <- compare_items(my_stats, items = items)
df[order(-df$dps), ]
```

If you want to know what impact world buffs have, simulate again.

```{r ony}
my_stats$crit <- my_stats$crit + 10
set.seed(42)
weights_ony <- compute_statweights(my_stats)
weights_ony
set.seed(42)
df_ony <- compare_items(my_stats, items = items)
df_ony[order(-df_ony$dps), ]
```

This can help setting your priorities right.
Note that this is only about the DPS and ignores survivability.
You might want to trade small a amount of DPS for stamina.
